What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2025-03-19 manuscript.Rmd
Addressing request re: Gorilla

Second, researchers need to take care with timing accuracy. Running studies on modern computers requires synchronizing multiple clocks, something that does not happen automatically. Failure to synchronize can result in substantial inaccuracies [@slim2022moving]. As indicated by the current work, the current jsPsych implementation of WebGazer.js has reasonably good timing synchronization. While it is possible that other Web-based eyetracking software achieves (or can achieve) the same level of precision as currently offered by jsPsych, we urge researchers to be cautious about using software for which the precision has not been documented.

Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background. We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.

>>>>

Second, researchers need to take care with timing accuracy. Running studies on mod.
ern computers requires synchronizing multiple clocks, something that does not happen automatically. Failure to synchronize can result in substantial inaccuracies [@slim2022moving]. As indicated by the current work, the current jsPsych implementation of WebGazer.js has reasonably good timing synchronization. We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.
Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background. We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.
